[Re] Non-additive coupling enables propagation of synchronous spiking activity in purely random networks

### 2018-03-06 article/Caze_2018.tex
Add V_0 to the parameter table

\begin{table}[ht]
\begin{tabular}{ l  c  S p{2.85cm}}
  \toprule
  {Parameter} & {Symbol} & {Value} &\\
  \midrule
  Number of neurons & $N$ & 1000 &\\
  Connection probability & $p_0$ & 0.3 &\\
  Probability connection being excitatory & $p_\text{ex}$ & 0.5 &\\
  Excitatory connection weight & $w_\text{ex}$ & \SI{0.2}{\milli\volt} & (varied in Fig.~\ref{fig:grid})\\
  Inhibitory connection weight & $w_\text{in}$ & \SI{0.2}{\milli\volt} & (varied in Fig.~\ref{fig:grid})\\
  Membrane time constant & $ \tau_m $ & \SI{8}{\milli\second} &\\
  Firing threshold & $\Theta$ & \SI{16}{\milli\volt} &\\
  Synaptic delay & $\tau$ & \SI{5}{\milli\second} & (but see Implementation section)\\
  Threshold for supra-linear summation & $V_a$ & \SI{2}{\milli\volt} \\
  Threshold for saturation & $V_b$ & \SI{4}{\milli\volt} \\
  Saturation value & $V_c$ & \SI{6}{\milli\volt} \\
  \bottomrule
\end{tabular}
\caption{Parameter values used in the simulations}\label{tab:parameters}
\end{table}

>>>>

\begin{table}[ht]
\begin{tabular}{ l  c  S p{2.85cm}}
  \toprule
  {Parameter} & {Symbol} & {Value} &\\
  \midrule
  Number of neurons & $N$ & 1000 &\\
  Connection probability & $p_0$ & 0.3 &\\
  Probability connection being excitatory & $p_\text{ex}$ & 0.5 &\\
  Excitatory connection weight & $w_\text{ex}$ & \SI{0.2}{\milli\volt} & (varied in Fig.~\ref{fig:grid})\\
  Inhibitory connection weight & $w_\text{in}$ & \SI{0.2}{\milli\volt} & (varied in Fig.~\ref{fig:grid})\\
  Membrane time constant & $ \tau_m $ & \SI{8}{\milli\second} &\\
  Firing threshold & $\Theta$ & \SI{16}{\milli\volt} &\\
  External input & $V_0$ & \SI{17.6}{\milli\volt}&(effect on $V$)\\
  Synaptic delay & $\tau$ & \SI{5}{\milli\second} & (but see Implementation section)\\
  Threshold for supra-linear summation & $V_a$ & \SI{2}{\milli\volt} \\
  Threshold for saturation & $V_b$ & \SI{4}{\milli\volt} \\
  Saturation value & $V_c$ & \SI{6}{\milli\volt} \\
  \bottomrule
\end{tabular}
\caption{Parameter values used in the simulations}\label{tab:parameters}
\end{table}
